### 2022-12-22 Draft_GFC.tex
Derniere version

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\usepackage{diagbox}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\usepackage{enumitem}
\newcounter{Ax}
\newcommand{\itemA}{%
    \addtocounter{Ax}{1}
    \item[A\theAx.]}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by 

@@

\item $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \mathbb{Z}^{2}$ the set of points in $S$
\item $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$,
\item for $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S.$
The $C_{m}(x)$ will be referred to as \textit{cells}. To ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$ and $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$.
Each $w \in \mathbb{E}^{(i)}_{m}$ is a segment of length $1$. 
\begin{remark} The cardinality of the set $\mathbb{E}^{\scriptscriptstyle  (i)}_{m}$
\label{cardEm}

@@

$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_1)\subset (0,m)^{2} \right\} $\\ 

@@

\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, (x, x+e_2)\subset (0,m)^{2} \right\} $\\ 

@@

Figure \ref{fig1} shows an example of a square tiling with~$m = 4$.

@@

@@

\paragraph{Discrete setting}

@@

Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$, each cell $C_{m}(x)$ is associated to black or white according to whether $Z^{\scriptscriptstyle (m)}_{t} (x) = 0$ or $Z^{\scriptscriptstyle (m)}_{t}(x)~= 1$. 

@@

For $t \in \mathbb{R}$, let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical. Let us consider the edge $w_{i}(x) := \left(x, x+e_{i}\right)$ with $i \in \{1,2\}$, $w_{i}(x)$ belongs to $C_{m}(x) \cap C_{m}(x-e_{j})$ with $i,j \in \{1,2\}$ and $i \neq j$ as soon as $w_{i}(x) \subset  \text{\larger[1]{$($}}0, m \text{\larger[1]{$)$}}^{2}$.

@@

\caption{The edge $w_{1} = (1,1)$ in red belongs to $C_{2}(0,0) \cap C_{2}(1, 0)$, with the cell $C_{2}(0,0)$ colored in black and $C_{2}(1, 0)$ in gray dashed stripes.}

@@

to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of $Z^{\scriptscriptstyle (m)}$.
\begin{Definition}[Directional perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical and horizontal). Then, the directional perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x: w_{i}(x) \in \mathbb{E}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).
\begin{Proposition}[First moment of the directional perimeter] 
with $N \sim \mathcal{N}(0,1)$. 
Note that $\mathbb{E}\left(f^{(i)}(t) \right) = 0$ in the case where $\rho(e_i) = 1$ 
Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis and Remark \ref{cardEm} one can write that, 
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right).
 with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$. Before going any further, let us first make the following remark, 

@@

\draw (4,0) node[below]{$\frac{b+a}{2}$};

@@

\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{b+a}{2}|$};

@@

@@

We start by applying to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$ the following transformation \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}, \end{equation*} 
the covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

\end{pmatrix}.$ \\
Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent. Hence, we can write

@@

\right.$ \linebreak with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 

@@

\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) \\
& = \mathbb{E}\left(\mathbbm{1}_{\left\{\min(X_{\scriptscriptstyle 0}, X_{e_i}) \leq t \leq \max(X_{\scriptscriptstyle 0}, X_{e_i})\right\}}\right) \\

@@

& = \mathbb{E}\left(\mathbbm{1}_{\left\{ - \sqrt{2(1-\rho(e_i))}\left|U\right| \leq  \sqrt{2(1+\rho(e_i)}V -2t \leq \sqrt{2(1-\rho(e_i))}\left|U\right| \right\}}\right) \\

@@

$$\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$

@@

\mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\

@@

Note that this result extends those given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 
\label{iidCase}
In the independent case \textit{i.e.} $\text{Cov}\left(X_{0}, X_i\right) = 0$, we can write

@@

\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) & = m(m-1)\mathbb{E}\left(\Phi\left(\sqrt{2}t + |Z|\right) - \Phi\left(\sqrt{2}t - |Z|\right)\right) = 2m(m-1)\Phi(t)\left(1-\Phi(t)\right) 
by applying the variable change {\small$\left\{\begin{array}{rcl}
u & = & \frac{y - z}{\sqrt{2}} \\
v & = & \frac{y+z}{\sqrt{2}} \\
\end{array}\right.$}, we get the same result as in \cite{Psymetrie} (Proposition \textcolor{blue}{3.1}).

@@

To have convergence when $m$ goes to infinity, one has to normalize the perimeter with the area of the window $S$, ($m^2$), thus considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.

@@

It is possible to link the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ to its perimeter, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$.}

@@

@@

\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance~$\rho$.}

@@

\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure, we  have the following result regarding their associated expected oriented perimeter at level $t$:}

@@

Let $t \in \mathbb{R}$ we can prove this result by considering  the function \begin{align*} 

@@

with $N \sim \mathcal{N}\left(0,1\right)$, its derivative is equal to 

@@

&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2|y| -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
&\hspace{5cm}\left. - \left(2|y| - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
& = \frac{\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}-2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
& = \frac{-2\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
& = \frac{-\exp(-t^2/(1+x))}{\pi\sqrt{(1-x^2)}},

@@

for all $|x| < 1, \; h'(x) < 0$ thus, $h$ is a strictly decreasing function. 

@@

\textcolor{red}{Thus, the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ is strictly decreasing, in particular if $\rho(e_1) \neq \rho(e_2) $\linebreak then~$\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$.\\ 
Now, if the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$. Thus, having a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$  would allow us to construct an isotropy test using the oriented perimeter of the field $X$.}

@@

In order to establish the CLT, we need to add some assumptions on $\rho$ the covariance structure of the field $X$.

@@

\begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold). We consider that $X_{x \in \mathbb{G}_{m}}$ a centered stationary standard Gaussian, let $r$ be a positive integer, $m \geq 2$ and $t_{1}, \cdots,t_{r} \in \mathbb{R}$, then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},

@@

@@

@@

\begin{proof} For the sake of simplicity, we will prove the CLT for $r=1$, the generalized case is made by following the same procedure. Using the Cramèr-Wold method, we need to prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have 

@@

Let us denote the 4-dimensional Gaussian vector by $\mathbb{X}_{x_1, x_2} = (X_{x_1, x_2}, X_{x_1 + 1, x_2}, X_{x_2, x_1+1}, X_{x_2, x_1} )$ and $g_{t} : \mathbb{R}^{4} \to \mathbb{R}$, 

@@

>>>>

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{amsmath,amssymb,amsthm,amsfonts,amstext,amsbsy,amscd,stmaryrd}
\usepackage{amssymb,amsmath,comment,subcaption,graphicx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{cancel}
\usepackage{tikz}
\usepackage{subcaption} 
\usetikzlibrary{patterns}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{float}
\usepackage{color}
\usepackage{relsize}
\usepackage{diagbox}
\newcommand{\modif}[1]{{\begin{modification}#1\end{modification}}}
\newcommand{\ele}[1]{{\color{red}#1}}
%\UseRawInputEncoding
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{mathrsfs}
\newcommand{\rmd}{{\mathrm{d}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\E}{\operatorname{\mathbb{E}}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\Cov}{\mathrm {Cov}}
\newcommand{\rme}{{\rm e}}
\renewcommand{\tilde}{\widetilde}
\renewcommand{\hat}{\widehat}
\newcommand{\TC}{\mathrm{TC}}
\newcommand{\TaC}{\mathrm{TaC}}
\newcommand{\LTC}{\mathrm{LTC}}
\newcommand{\LP}{\mathrm{LP}}
\newcommand{\Per}{\mathrm{Per}}
\theoremstyle{Theorem}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
\newtheorem{Definition}[Theorem]{Definition}
\theoremstyle{definition}
\newtheorem{remark}{Remark}
\renewcommand{\labelitemi}{\textperiodcentered}
\allowdisplaybreaks
\usepackage{ifpdf}
\ifpdf
\else
\usepackage{graphicx}
\DeclareGraphicsExtensions{.eps,.jpg,.png}
\fi
\usepackage{epstopdf}
\usepackage{array}
\usepackage{enumitem}
\newcounter{Ax}
\newcommand{\itemA}{%
    \addtocounter{Ax}{1}
    \item[A\theAx.]}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

@@

Let $m$ be an integer with $m \geq 2$. Without loss of generality, we consider our observation window as the unit square $S = [0,m]^{2}$ and  we divide our window into $m^{2}$ pairwise disjoint squares. We denote by $e_1$, $e_{2}$ the elements of the canonical base of $\mathbb{R}^{2}$ and 

@@

 \item[$\bullet$] $\mathbb{G}_{m} := \text{\larger[1]{$[$}}0, m \text{\larger[1]{$)$}}^{2} \cap \, \mathbb{Z}^{2}$ the set of points in $S$, to ease up the notations we write $x = (x_1, x_2)$ with $x_1, x_2 \in \{0,\ldots, m-1\}$ for any $x\in \mathbb{G}_{m}$.
 \item[$\bullet$] For $x\in \mathbb{G}_{m}, \; C_{m}(x) \, := \,x + \text{\larger[1]{$[$}}0, 1 \text{\larger[1]{$]$}}^{2} \subset S$, the $C_{m}(x)$ will be referred to as \textit{cells}.
\item[$\bullet$] And finally, we denote by  $\mathbb{E}^{(1)}_{m}, \; \mathbb{E}^{(2)}_{m} $ the set of vertical and horizontal edges in $\mathring{S}$, for each $x \in \mathbb{G}_{m}$,  $i \in \{1, 2\}$, the edge $w_{i}(x)$ is a segment of length $1$ and belongs to~$C_{m}(x) \cap C_{m}(x+e_{i})$. The cardinality of the sets of edges

@@

$\left\{ x \in \mathbb{G}_{m}; w_{1}(x) \in \mathbb{E}^{\scriptscriptstyle  (1)}_{m}\right\} = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{1}(x) \in C_{m}(x) \cap C_{m}(x+e_{1})\right\} $\\ 

@@

\item$\left\{ x \in \mathbb{G}_{m}; w_{2}(x) \in \mathbb{E}^{\scriptscriptstyle  (2)}_{m}\right\}  = \left\{x \in \llbracket 0, m-1 \rrbracket^{2}, w_{2}(x) \in C_{m}(x) \cap C_{m}(x+e_{2}) \right\} $\\ 

@@

Figure \ref{figure1} shows an example of a square tiling with~$m = 4$.

@@

\label{figure1}

@@

\vspace{-1cm}
\paragraph{Discrete setting and binary image}

@@

Considering a threshold parameter $t \in \mathbb{R}$, we introduce the associated binary \linebreak image $Z^{\scriptscriptstyle (m)}_{t} = \left(\mathbbm{1}_{\left\{X_x \geq t\right\}} \right)_{x \in \mathbb{G}_{m}}$ where each cell $C_{m}(x)$ is associated to black or white according to whether~$X_{x} \geq t$ or $X_{x} \leq t$. 

@@

For $t \in \mathbb{R}$, let $Z^{\scriptscriptstyle (m)} = Z^{\scriptscriptstyle (m)}_{t}$ be the  binary image at that given threshold $t \in \mathbb{R}$. Following  the approach  presented in \cite{HermineAgnes},  for each edge $w \in \mathbb{E}_{m}$, we aim to know if  $w$ contributes  to the perimeter of the black component of $Z$. Making use of the additive nature of the perimeter, one can start by computing the oriented perimeter given each direction, horizontal and vertical.

@@

\caption{The edge $w_{1}(0,0)$ in red belongs to $C_{2}(0,0) \cap C_{2}(1, 0)$, with the cell $C_{2}(0,0)$ colored in black and $C_{2}(1, 0)$ in gray dashed stripes.}

@@

to compute the contribution of the edge $w_i(x)$ to the perimeter of the black component of~$Z^{\scriptscriptstyle (m)}$. Before stating the definition of the oriented perimeter let us first make an observation that will appear very useful in the rest of the paper.  

@@

\draw (4,0) node[below]{$\frac{a+b}{2}$};

@@

\node[text width= 0.7cm, font=\large] at (3,-1) {$|t -~\frac{a+b}{2}|$};

@@

\vspace{-1cm}

@@

\begin{Definition}[Oriented perimeter of a binary image $Z^{\scriptscriptstyle (m)}$]\label{defPerimetre}~\\
For $t\in \mathbb{R},$ we denote by $\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t)$ the sum of all contributions over the $i$th direction (vertical for $i = 1$ and horizontal for $i = 2$). Then, the oriented perimeter of the binary image $Z^{\scriptscriptstyle (m)}$ is given by
\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) =~\sum_{\scriptscriptstyle x \in \mathbb{G}^{\scriptscriptstyle (i)}_{m}} f_{t}^{\scriptscriptstyle (i)}(x).
\begin{Proposition}[First moment of the oriented perimeter] 
with $N \sim \mathcal{N}(0,1)$ and $\Phi$ being the cumulative distribution function of the standard Gaussian. 
Let us assume that $\rho(e_{i}) \in ]-1,1]$. Considering the formula for $\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t)$ and applying the stationarity hypothesis one can write that, 
\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) = m(m-1)\mathbb{E}\left(f^{(i)}(t)\right),
 with $\mathbb{E}\left(f^{(i)}(t)\right) = \mathbb{P}\left(\min\left(X_{\scriptscriptstyle 0}, X_{e_i}\right) < t \leq \max\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)\right)$.
We start by applying the following transformation to the Gaussian vector $\left(X_{\scriptscriptstyle 0}, X_{e_i}\right)$,  \begin{equation*} \label{expressions} \Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} - X_{\scriptscriptstyle 0}, \hspace{0.5cm} S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0} := X_{e_i} + X_{\scriptscriptstyle 0}. \end{equation*} 
The covariance matrix of the new Gaussian vector $\left(\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}, S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}\right)$ is given by ${\tilde{\Sigma}_{i}(0)~= M\Sigma_{i}(0) M^{\star}}$ with {\small $M = \begin{pmatrix}

@@

\end{pmatrix}.$ Thus, $\tilde{\Sigma}_{i}(0) = \begin{pmatrix}  2(1-\rho(e_i)) & 0 \\ 0 & 2(1+\rho(e_i)  \end{pmatrix}$, which directly  implies that the two variables~$\Delta^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ and $S^{\scriptscriptstyle (i)}_{\scriptscriptstyle 0}$ are independent. Hence, we can write

@@

\right.$ with~$(U, V) \sim \mathcal{N}\left(0, I_{2}\right)$. Thus, applying Remark \ref{lemmasommediff} above we get 

@@

\mathbb{E}\left(f^{(i)}(t)\right) 

@@

@@

$$\mathbb{E}\left(f^{\scriptscriptstyle (i)}(t)\right) = \mathbb{E}\left(\Phi\left(\dfrac{2t + \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)  - \Phi\left(\dfrac{2t - \sqrt{2(1-\rho(e_i))}|N|}{\sqrt{2(1+\rho(e_i))}}\right)\right).$$

@@

\mathbb{E}\left(f^{(i)}(t)\right) & = \mathbb{P}\left(\min\left(N, -N\right) < t \leq \max\left(N, -N\right)\right) \\

@@

This result extends the one given in \cite{HermineAgnes} (Proposition 3) since we do not assume here that $\rho(e_i) > 0$. 
\begin{remark}(Degenerate dependence cases.)
\item In the case of a fully dependent field, \textit{i.e}  $\rho(e_i) = 1$, note that $\mathbb{E}\left(\mathcal{P}_{m}^{\scriptscriptstyle (i)}(t) \right) = 0$.
\item In the independent case, \textit{i.e.} $\rho(e_{i}) = \text{Cov}\left(X_{0}, X_{e_i}\right) = 0$, we can write

@@

\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle  (i)}_{m}(t) \right) & = m(m-1)\mathbb{E}\left(\Phi\left(\sqrt{2}t + |N|\right) - \Phi\left(\sqrt{2}t - |N|\right)\right) = 2m(m-1)\Phi(t)\left(1-\Phi(t)\right), 
\end{align*}}by applying the variable change $ (y, z) \mapsto (\frac{y-z}{\sqrt{2}}, \frac{y+z}{\sqrt{2}})$ to get the second identity. We get the same result as in \cite{Psymetrie} (Proposition \textcolor{blue}{3.1}). \\ As in \cite{Psymetrie} in order to converge towards a non degenerate quantity when $m$ goes to infinity, we have to consider a normalized perimeter thus, dividing the perimeter by the area of the window $S$, considering $\frac{1}{m^2}\mathcal{P}_{m}(t)$.

@@

\paragraph{Total variation.}

@@

In image processing, the total variation of an image $u \in L^{1}_{loc}(\Omega)$ which is given by $\int_{\Omega}|\nabla u|dx$ is a common and well studied object. It is possible to link this quantity the perimeter of $u$, by applying the coarea formula, $\int_{\Omega}|\nabla u|dx = \int_{\mathbb{R}}\mathcal{P}(t)dt$ with $\mathcal{P}(t)$ being the perimeter associated to the level set of the image $u$ at level $t$. In the following result, by considering Proposition \eqref{propFisrtmoment}, we obtain a simple expression for the first moment of the total variation, and link it directly to the covariance evaluated in the $i$th direction.}

@@

\label{Variationtotal}

@@

\textcolor{red}{Let us now study the monotonic properties of the function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ where $\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}$ is the perimeter with respect of the orientation $i$ associated to the Gaussian field of covariance function $\rho$. This result allows us to state that the oriented perimeter is a strictly decreasing function with respect to $\rho$. }

@@

\textcolor{red}{Let $\overline{X}, \tilde{X}$ be two stationary centered Gaussian random fields with unit variance, and $\bar{\rho}, \tilde{\rho}$ their respective covariance structure. For any level $t$, we  have the following result:}

@@

Let $t \in \mathbb{R}$, We consider the function $h$ defined as follow \begin{align*} 

@@

with $N \sim \mathcal{N}\left(0,1\right)$. The derivative of $h$ is equal to 

@@

&\hspace{0.5cm} \int_{0}^{\infty}\left(\left(-2y -t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y+t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right. \\
&\hspace{5cm}\left. - \left(2y - t\sqrt{2(1-x)}\right)\exp\left(-\frac{\left(y-t\sqrt{2(1-x)}/2\right)^{2}}{1+x}\right)\right)dy \\
& = \frac{-\exp(-t^2/(1+x))}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\exp\left(\frac{t^2(1-x)}{2(1+x)}\right)\\
& \hspace{2cm} \left(\int_{\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz + \int_{-\frac{t}{2}\sqrt{2(1-x)}}^{\infty}2z\exp\left(-\frac{z^2}{1+x}\right)dz \right)\\
& = \frac{-\exp(-t^2/(1+x))(1+x)}{2\pi(1-x)^{1/2}(1+x)^{3/2}}\\
& = \frac{-\exp(-t^2/(1+x))}{2\pi\sqrt{(1-x^2)}}.

@@

Since for all $|x| < 1, \; h'(x) < 0$, $h$ is a strictly decreasing function. 

@@

\label{remarkesperancetest}
\textcolor{red}{The function $\rho \mapsto \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (i)}_{m, \rho}(t)\right)$ being strictly decreasing, if $\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right) \neq \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)$ then~$\rho(e_1) \neq \rho(e_2) $. Now, assume that the field $X$ is isotropic, one consequence would be that $\rho(e_{1}) = \rho(e_{2})$ which implies~$\frac{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)}{\mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)} = 1$. Then, the ratio $\mathcal{P}^{\scriptscriptstyle  (1)}_{m}(t)/\mathcal{P}^{\scriptscriptstyle  (2)}_{m}(t)$ would be distributed around $1$ in the case of isotropy. This consideration will be crucial for the proposed local isotropy testing procedure in the next section.}

@@

\label{isotest}
In order to construct a local isotropy test using the oriented perimeter of the field $X$, we first  establish a Central Limit Theorem for the variable $\mathcal{P}^{\scriptscriptstyle (i)}_{m}(t)$. To do that, we have to add some assumptions on $\rho$ the covariance structure of the field $X$.

@@

\begin{Theorem}\label{TCL}(Multi-directional multivariate CLT for r-threshold). We consider that $(X_{x})_{x\in \mathbb{G}_{m}}$ is a centered stationary standard Gaussian field. Let $r$ be a positive integer and $t_{1}, \cdots,t_{r} \in \mathbb{R}$. Then, under \textbf{$(A_{1})$} and \textbf{$(A_{2})$},

@@

\label{CovTCL}
\begin{proof} For the sake of simplicity, we will prove the theorem for $r=1$, the generalized case can be established by following the same procedure. Using the Cramèr-Wold method, we will prove that for each $(a_1, a_2) \in \mathbb{R}^{2}$, we have 

@@

\frac{a_{1}}{m}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (1)}_{m}(t)\right)\right) + \frac{a_{2}}{m}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t) - \mathbb{E}\left(\mathcal{P}^{\scriptscriptstyle (2)}_{m}(t)\right)\right) \xrightarrow[m \to \infty]{d} \mathcal{N}\left(0,\,\sigma^{2}(t)\right) 

@@

with $\sigma^{2}(t) < \infty$. Let~$ t \in \mathbb{R}$, $x=(x_{1}, x_{2}) \in \mathbb{G}_{m}$ and $i \in \{1,2\}$, we recall the notation introduced in \eqref{fi}

@@

so that, re-writing the sum we get

@@

\begin{Lemma}(Computation of the two cells contribution)
